### 2019-03-01 sections/example.tex
fixed minor nits in example section

Now we develop our workflow in a top down way.
Our flight booking starts with an interactive task \TS{enter (List Passenger)}, where users can enter a list of passengers.
A task $\Enter \tau$ is an empty editor that asks for a value of the given type $\tau$.
Passengers are valid if their name is not empty and their age is at least 0.
Lists of passengers are valid if each passenger is valid, and at least one of the passengers is an adult.
When the user has entered a valid list of passengers, the step after \TS{>>?} becomes enabled,
and the user can proceed to picking seats.
\begin{TASK}
  let valid = \p. not (fst p == "") /\ snd p >= 0 in
  let adult = \p. snd p >= 18 in
  let allValid = \ps. all valid ps /\ any adult ps in
  let bookFlight = enter (List Passenger) >>? \ps.
    if allValid ps then chooseSeats ps else fail
\end{TASK}
A selection of seats is correct if every entered seat is free.
\begin{TASK}
  let correct = \ss. intersect ss !freeSeats == ss in
  let chooseSeats = \ps. enter (List Seat) >>? \ss.
    if correct ss /\ length ps == length ss then confirmBooking ps ss else fail
\end{TASK}

The function \TS{confirmBooking} removes the picked seats from the shared list of free seats,
and displays the end result using an editor, denoted by \TS{edit}.
\begin{TASK}
  let confirmBooking = \ps. \ss.
    freeSeats := difference !freeSeats ss; edit <<ps, ss>>
\end{TASK}
% It uses a function \TS{difference}, which removes all elements from the second list from the first list.

>>>>

Now we develop our workflow in a top-down manner.
Our flight booking starts with an interactive task \TS{enter (List Passenger)}, where users can enter a list of passengers.
A task $\Enter \tau$ is an empty editor that asks for a value of the given type $\tau$.
Passengers are valid if their name is not empty and their age is at least 0.
Lists of passengers are valid if each passenger is valid, and at least one of the passengers is an adult.
When the user has entered a valid list of passengers, the step after \TS{>>?} becomes enabled,
and the user can proceed to picking seats.
\begin{TASK}
  let valid = \p. not (fst p == "") /\ snd p >= 0 in
  let adult = \p. snd p >= 18 in
  let allValid = \ps. all valid ps /\ any adult ps in
  let bookFlight = enter (List Passenger) >>? \ps.
    if allValid ps then chooseSeats ps else fail
\end{TASK}
A selection of seats is correct if every entered seat is free.
\begin{TASK}
  let correct = \ss. intersect ss !freeSeats == ss in
  let chooseSeats = \ps. enter (List Seat) >>? \ss.
    if correct ss /\ length ps == length ss then confirmBooking ps ss else fail
\end{TASK}

The function \TS{confirmBooking} removes the selected seats from the shared list of free seats,
and displays the end result using an editor, denoted by \TS{edit}.
\begin{TASK}
  let confirmBooking = \ps. \ss.
    freeSeats := difference !freeSeats ss; edit <<ps, ss>>
\end{TASK}
% It uses a function \TS{difference}, which removes all elements from the second list from the first list.
